---
title: "Weight of Fish"
author: "Tanya Claros"
date: "Summer 2022"
output: 
  html_document:
    number_sections: true
    toc: true
---



```{r include=FALSE,echo=FALSE}
require(tigerstats)
require(tidyverse)

Fish = read.csv("Fish.csv")
Perch = filter(Fish, Species == "Perch")
Pike = filter(Fish, Species == "Pike")
Roach = filter(Fish, Species == "Roach")
```

# Predicting Fish Weight

## Perch

```{r}

pwt =  lm(Weight~ Length1 + Length2 + Length3 + Height, data = Perch)
summary(pwt)
```

```{r}
library(leaps)
regsubsets.out <-
    regsubsets(Weight ~ Length1+ Length2 + Length3 + Height,
               data = Perch,
               nbest = 2,       # 1 best model for each number of predictors
               nvmax = NULL,    # NULL for no limit on number of variables
               force.in = NULL, force.out = NULL,
               method = "exhaustive")
regsubsets.out
```

```{r}
summary.out <- summary(regsubsets.out)
as.data.frame(summary.out$outmat)
```

### Best Models

The best two predictors of wt for Perch are Length3 and Height.


### Best Two regressor model

From the graph the best two-paramator regressor model is based on Length3 and Height.


## Pike
```{r}

pwt =  lm(Weight~ Length1 + Length2 + Length3 + Height, data = Pike)
summary(pwt)
```

```{r}
library(leaps)
regsubsets.out <-
    regsubsets(Weight ~ Length1+ Length2 + Length3 + Height,
               data = Pike,
               nbest = 2,       # 1 best model for each number of predictors
               nvmax = NULL,    # NULL for no limit on number of variables
               force.in = NULL, force.out = NULL,
               method = "exhaustive")
regsubsets.out
```

```{r}
summary.out <- summary(regsubsets.out)
as.data.frame(summary.out$outmat)
```


### Best Models

The best model is the one that uses all the variables. Length1, Length2, Length3 and Height.

### Best Two regressor model

The best two regressor model is Length1 and Length3.

## Roach

```{r}

pwt =  lm(Weight~ Length1 + Length2 + Length3 + Height, data = Roach)
summary(pwt)
```

```{r}
library(leaps)
regsubsets.out <-
    regsubsets(Weight ~ Length1+ Length2 + Length3 + Height,
               data = Roach,
               nbest = 2,       # 1 best model for each number of predictors
               nvmax = NULL,    # NULL for no limit on number of variables
               force.in = NULL, force.out = NULL,
               method = "exhaustive")
regsubsets.out
```

```{r}
summary.out <- summary(regsubsets.out)
as.data.frame(summary.out$outmat)
```

### Best Models

The best model is the one that uses all the variables. Length1, Length2, Length3 and Height.

### Best Two regressor model

The best two regressor model is Length1 and Length3.

## Final Summary Statements
The best two predictors of wt for Perch are Length3 and Height. From the graph the best two-paramator regressor model is based on Length3 and Height. The best model is the one that uses all the variables. Length1, Length2, Length3 and Height for Pike. The best two regressor model is Length1 and Length3. And lastly for Roach the best model is the one that uses all the variables. Length1, Length2, Length3 and Height. The best two regressor model is Length1 and Length3.